\Large\bf Data Intensive processing with iRODS and the middleware CiGri for the Whisper project

### 2014-06-13 articles/2014/whisper/aricleEbauche/articleIrodsUserMeeting.tex
Redaction (brouillon) de la partie results/IT

>>>>

With the Whisper project, as with some few other projects, we had the opporunity to test and improve the CIMENT IT infrastructure for a data-intensive case. In this kind of projects, data management and input/output data flows are a big part of the process regarding the actual computing time for the analysis. With a grid of several thousands cpu-cores, such a project may act as a real distributed attack against our storage infrastructures! So, as a first consequence of the deployment of such computing jobs, we had to implement new "limiting" functionnalities into our infrastructure softwares or configurations. For example, CiGri is able to limit the number of submitted jobs for a given campaign on a given cluster if we know that the jobs concurrency can overload our Irods infrastructure. As another example, iRODS may be configured to limit the number of simultaneous connections. But in this case, the i-command returns with an error and the job may be aborted. There's a "--retry" optionnal argument, but with a high level of concurrency, it increases the load and may completely exhaust the servers with a ton of retry queries. We then developped a wrapper for the i-commands, called secure-i-commands that implements a retry on some specific error cases  with an incremental delay to prevent from flooding the irods servers. Of course, this can be improved as this leads to a waste of computing resources because they are reserved and not used while waiting. But this is at least a security improvement in case the highler level decision processes does not work as expected because of their high complexity.
\\
Regarding the iRODS choice, it was made on the features: we need a distributed file system suitable for a distributed and heterogeneous grid infrastructure composed of several supercomputers having gateways to reach each-other; and we need a unique namespace. We also need the sites to be independent of the others. It means that a site can be out of service, the data available in another site should still be available. The only case when the entire infrastructure is broken is when the centralized meta-catalog is not reachable. But this part of the infrastructure is located in a highly available datacenter and we may also implement a HA meta-catalog. As it is not posix compliant, iRODS allows more control for the admins and the users. For example, replication can be completely controlled. In our case, we do an automatic replication (staging) of the files when they are got from site A or B to site C, for network optimization. But the user may also want to replicate on every sites to get better performances with big jobs campaigns spread on every clusters of the grid. 
Also better than a posix filesystem, the users can add custom meta-data to the files and collections allowing them to retrieve data by making some queries with an SQL-like syntax. 
\\
Another interesting aspect of iRODS for a project like Whisper is that we can register into iRODS data that are stored on a dedicated posix filesystem. For example, the Japanese raw data were stored on external storage disks that we copied through USB directly onto a server dedicated to the project. We then added this server as an iRODS resource and then registered the data to make them available to the whole grid. In this example, we also used the access rules to set up a read/write policy for the only concerned users.
\\\textbf{Open problems and future works}
\\
\begin{itemize}
  \item Irods has a different transfert policy for "small" files (under 32MB). In this case, files are transiting through the server used by the client instead of a direct connection between the original resource and the client. In a high load context, with a lot of small file transfers, it leads to an overload of the concerned server. A possible solution to that problem could be to share the load among the servers of a given site. For that, we can imagine using a virtual ip address making a round robind on all the ip addresses of the servers of the site.
  \item Network overload with automatic staging
  \item Using pyrods
\end{itemize}
